### 2023-09-13 main.tex
sequence of similarity

@@

	H\;\xrightarrow{S_{1}}\;H^{'}\;\xrightarrow{S_{2}}\;H^{''}

@@

   H^{'}=S_{1}H^{'}S_{1}^{-1}

@@

Describe eigenvalues of $T_0$ following 
\cite{Belliard2} 
\section{Extensions for the non-integrable chain}
The aim of this section is studying some extension to the analysis previously done when integrability property is lost. 
In particular, Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.  
This nice property is lost when we allow an arbitrary maximal occupation $\nu>1$. For the sake of simplicity we still study the geometry of chain and we provide the following extensions: 
\begin{enumerate}
	\item \textit{Arbitrary correlations}: exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles. These probability are hard to find in this partial exclusion situation, however correlation can be formally written. Subsection \ref{Subsection-ss-nonI}.
	\item \textit{Instantaneous thermalization}: starting from the multi-species stirring dynamics, we can define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond. Subsection \ref{Subsection-Thermalized}.
	\item \textit{Reaction-diffusion process}: a further dynamics is added. Particle can now change type. The model is constructed with the goal of having the average density evolving a system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}. Subsection \ref{Subsection-RD}
\end{enumerate}

@@

In \cite{casini2022uphill} it has been defined a process whose evolution equation for the average occupation $\rho_{a}(x,t)$ of species $a\in \{2,3\}$ is given by a difference-differential equation with two discrete Laplacians (one for each species, multiplied for a proper diffusivity constant) and a linear reaction term (mutation), i.e.

@@

for $ x\in\{1,\ldots,L\}\quad a\in\{2,3\}$  and where $\overline{a}=3$ if $a=2$ and $\overline{a}=2$ if $a=3$.

>>>>

\begin{equation}\label{definition-SteadyStateH}

@@

	H\;\xleftrightarrow{S_{1}}\;H^{'}\;\xleftrightarrow{S_{2}}\;H^{''}

@@

   H^{'}=S_{1}HS_{1}^{-1}

@@

Describe eigenvalues of $T_0$ following 
\cite{Belliard2} 
\subsection{A sequence of similarity transformation}
In Subsection \ref{subsection-exact} and \ref{SectionNonLocalTrasformation} we have found three similarity transformations, namely $S_{1}$, $S_{2}$ and $W$ between operators $H$, $H^{'},H^{''}$ and $H_{0}$. Using them simultaneously one can map the non-equilibrium Hamiltonian $H$ onto the equilibrium one as
	H\;\xleftrightarrow{S_{1}}\;H^{'}\;\xleftrightarrow{S_{2}}\;H^{''}\xleftrightarrow{W}\;H_{0}
More explicitly we have 
	H_{0}=W^{-1}\,S_{2}\,S_{1}\,H\,S_{1}^{-1}\,S_{2}^{-1}\,W
as a consequence we have that, for a fixed configuration $\bm{m}$, the non-equilibrium eigenvectors can be mapped to the equilibrium ones as
	|\Psi_{\bm{m}}\rangle=S_{1}^{-1}S_{2}^{-1}W|\Psi_{\bm{m}}^{0}\rangle
and using \eqref{SteadyState-W-Good} the steady state of $H$ defined in \eqref{definition-SteadyStateH} can be obtained from the vacuum state $|\Psi_{0}^{0}\rangle$ defined in \eqref{Vacuum-state} as
	|\Psi\rangle=&\text{exp}\left(-\sum_{x=1}^{L}\sum_{a=1}^{N-1}e_{Na}^{x}\right)\text{exp}\left(\sum_{x=1}^{L}\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)\\&
	\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{(\alpha_{1}-\beta_{1})^{k_{1}}\cdots (\alpha_{N-1}-\beta_{N-1})^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\\&
\section{Extensions for the non-integrable chain}
The aim of this section is studying some extension to the analysis previously done when integrability property is lost. 
In particular, Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.  
This nice property is lost when we allow an arbitrary maximal occupation $\nu>1$. For the sake of simplicity we still study the geometry of chain and we provide the following extensions: 
	\item \textit{Arbitrary correlations}: exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles. These probability are hard to find in this partial exclusion situation, however correlation can be formally written. Subsection \ref{Subsection-ss-nonI}.
	\item \textit{Instantaneous thermalization}: starting from the multi-species stirring dynamics, we can define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond. Subsection \ref{Subsection-Thermalized}.
	\item \textit{Reaction-diffusion process}: a further dynamics is added. Particle can now change type. The model is constructed with the goal of having the average density evolving a system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}. Subsection \ref{Subsection-RD}

@@

In \cite{casini2022uphill} it has been defined a process whose evolution equation for the average occupation $\rho_{a}(x,t)$ of species $a\in \{1,2\}$ is given by a difference-differential equation with two discrete Laplacians (one for each species, multiplied for a proper diffusivity constant) and a linear reaction term (mutation), i.e.

@@

for $ x\in\{1,\ldots,L\}\quad a\in\{1,2\}$  and where $\overline{a}=1$ if $a=2$ and $\overline{a}=1$ if $a=2$.
